Laplacian envelope

### 2021-09-01 Notes/laplace.tex
M to W in finite time section

If the plasticity events occur at Poisson rate \(r\), the probability of \(n\) events occurring in time \(t\) is given by a Poisson distribution with mean \(rt\).
If we marginalise over \(n\) as well
%
\begin{equation}\label{eq:plastseqav}
\begin{aligned}
  P(\text{state}=i,t \mid \text{pot/dep},0)
    &= \sum_n \frac{(rt)^n}{n!} \e^{-rt} \eq  \MMd \potdep (f\pot \MMd \pot+f\dep \MMd \dep)^n \\
    &= \brk{ \eq  \MMd \potdep\, \e^{rt(f\pot \MMd \pot+f\dep \MMd \dep-\I) } }_i,
\end{aligned}
\end{equation}
%
where \(\eq\) is the steady state distribution of the continuous time transition matrix that appears in the exponential:
%
\begin{equation}\label{eq:eq}
  \eq\frg = 0,
  \qquad\text{where}\quad
  \frg = \sum_\nu r f^\nu (\MMd^\nu - \I)
    = r f\pot \MMd \pot + r f\dep \MMd \dep - r \I.
\end{equation}
%

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\synid^1 \syn^1(t)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \e^{t\frg} \w, \\
  \av{\synid^1 \syn^1(\infty)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  \Delta f\, \eq \e^{t\frg} \w ,
\end{aligned}
\end{equation}
%
where \(\Delta f = f\pot - f\dep \).
Combining the expressions in \cref{eq:overlapwt} allows us to write the numerator of \cref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\synid \cdt \syn(t)} - \av{\synid \cdt \syn(\infty)}
    &= \frac{N}{r} \eq \enc \, \e^{t \frg} \w , \\
    \text{where} \qquad
  \enc &= \sum_\nu (-1)^\nu r f^\nu (\MMd^\nu - \I)
    = r f\pot \MMd\pot - r f\dep \MMd\dep - r \Delta f \I.
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{t \frg}\w}
                 {r \sqrt{1-(\Delta f)^2(\eq \w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with \(f\pot=f\dep\) or \(\eq_+=\eq_-\).
We can perform the maximisation in two steps.
First maximise the numerator at fixed \(\eq \w\).
Then maximise the ratio \wrt \(\Delta \pr = \eq\w\).
This will allow us to ignore the denominator until the very end.

We can then treat the off-diagonal elements of \(\MMd^\nu\) as the independent degrees of freedom, subject to these constraints, when maximising the SNR.
The diagonal elements are determined by setting the row sums to 1.
We then have
%
\begin{equation}\label{eq:derivpd}
  \pdiff{\MMdm^\mu_{ij}}{\MMdm^\nu_{mn}} 
      = \delta_{\mu\nu}\, \delta_{im}(\delta_{jn}-\delta_{jm}),
\end{equation}
%
It will also be convenient to define the differential operators
%
\begin{equation}\label{eq:pertfe}
  \pdiff{}{\frgm_{ij}} = \frac{1}{2rf\pot} \pdiff{}{\MMdm \pot_{ij}} + \frac{1}{2rf\dep} \pdiff{}{\MMdm \dep_{ij}},
  \qquad
  \pdiff{}{\encm_{ij}} = \frac{1}{2rf\pot} \pdiff{}{\MMdm \pot_{ij}} - \frac{1}{2rf\dep} \pdiff{}{\MMdm \dep_{ij}},
\end{equation}
%
these satisfy
%
\begin{equation}\label{eq:derivfe}
  \pdiff{\frgm_{ij}}{\frgm_{mn}} = \pdiff{\encm_{ij}}{\encm_{mn}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\frgm_{ij}}{\encm_{mn}} = \pdiff{\encm_{ij}}{\frgm_{mn}} = 0.
\end{equation}
%

If we wish to use the off-diagonal elements of \(\frg\) and \(\enc\) as the degrees of freedom, the constraints are
%
\begin{equation}\label{eq:constrfe}
\begin{aligned}
  \frgm_{i \neq j}   &\geq \abs{ \encm_{i \neq j} }, &\qquad
  \sum_{j\neq i}\frgm_{ij} + (-1)^\mu \encm_{ij}  &\leq 2rf^\mu, \\
  \sum_j \frgm_{ij} &=0, &
  \sum_j \encm_{ij} &=0.
\end{aligned}
\end{equation}
%

@@

We can also express this in terms of the shifted process in \cref{eq:larea}.
We can choose how to distribute the shift across \(\MMd \pot\) and \(\MMd \dep\).
Two choices from a continuum%
\footnote{We could choose \( \shift{\MMd}^\nu(s) = \MMd^\nu + \frac{s g^\nu}{r f^\nu} (\onev \eq - \I) \), for any \(g^\nu \) with \( \sum_\nu g^\nu = 1 \).
It shifts \(\frg\) correctly and also shifts \( \shift{\enc}(s) = \enc + \frac{s}{r} \Delta g (\onev \eq - \I) \).
The two possibilities in \cref{eq:lshiftpd} come from \(g^\nu = \frac{1}{2}\) and \(g^\nu = f^\nu\) respectively.}
are:
%
\begin{equation}\label{eq:lshiftpd}
  \shift{\MMd}^\nu(s) = \MMd^\nu + \frac{s}{2 r f^\nu} (\onev \eq - \I)
  \qquad \text{or} \qquad
  \shift{\MMd}^\nu(s) = \MMd^\nu + \frac{s}{r} (\onev \eq - \I).
\end{equation}
%
The first choice leaves \( \shift{\enc} = \enc \), so it only affects the \(\etw\) piece of \cref{eq:larea}.
The second choice does not leave \(\enc\) invariant (in fact \( \shift{\enc}(s) = \enc + \frac{s}{r} \Delta f (\onev \eq - \I) \)), but because \( \eq (\onev \eq - \I) = 0 \) the shift does not make any contribution to \cref{eq:larea}.
Either way:
%
\begin{equation}\label{eq:lareashift}
  \hat{A}\prn{s; \MMd^\nu} = \hat{A}\prn{0; \shift{\MMd}^\nu(s)}.
\end{equation}
%
In other words, the laplace transform of the SNR is the area under the SNR for the shifted process.

Note that while \cref{eq:lshift} produces a valid continuous-time Markov process, \cref{eq:lshiftpd} does not always produce valid discrete-time Markov processes, as the diagonal elements can become negative.
However, \(r (\shift{\MMd}^\nu - \I)\) is a valid continuous-time Markov process.

@@

Now we'll maximise \(\snrb(\tau)\) for some fixed \(\tau\), subject to the constraints \eqref{eq:constr}.
First, we will maximise the numerator of \eqref{eq:lsnr} holding \(\eq\w\) fixed.
We can maximise the ratio \wrt \(\eq\w\) later.
From this point on, we work in units where \(r = 1\).

Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i(s) - \etwm_j(s))
        +\sum_{\nu i j} { r f^\nu \mu^\nu_{ij} \MMdm^\nu_{ij} }
        + \lambda \prn{ \Delta\pr - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where \(\Delta\pr\) is the constant value we are holding \(\eq\w\) at.
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\MMdm^\nu_{ij}} = 0, \quad
  \mu^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu^\nu_{ij}} \geq 0, \quad
  \mu^\nu_{ij}\pdiff{\CL}{\mu^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
We have scaled the KKT multipliers by \(r f^\nu\) for later convenience.

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{rf^\nu} \pdiff{\CL}{\MMdm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     + \prn{c_m(s) + (-1)^\nu} \brk{\etwm_m(s) - \etwm_n(s)} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     + \lambda \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
We can solve for the KKT multipliers by noting that
%
\begin{equation*}
  \mu^\nu_{ij} \MMdm^\nu_{ij} = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \mu^\nu_{ii} \MMdm^\nu_{ij} 
      = \mu^\nu_{ii} (1 - \MMdm^\nu_{ii}) = \mu^\nu_{ii}.
\end{equation*}
%
Then, with some new vectors defined:
%
\begin{equation}\label{eq:kktsol}
\begin{aligned}
  \mu^\nu_{mm} &= - \eqm_m \prn{ \albm^\nu_m(s) 
    + \lambda \ombm^\nu_m(0) 
    + \prn{{c}_m(s) + (-1)^\nu} \ombm^\nu_m(s)
    }, \\
  \mu^\nu_{mn} &= \eqm_m \big( 
      \brk{ \thbm_n(s) - \thbm_m(s) - \albm^\nu_m(s) }
    + \lambda \brk{ \etwm_n(0) - \etwm_m(0) - \ombm^\nu_m(0) } 
  \\ &\hphantom{= \eqm_m \big( }
    + \brk{{c}_m(s) + (-1)^\nu} 
        \brk{ \etwm_n(s) - \etwm_m(s) - \ombm^\nu_m(s) }
     \big), \\
  \text{where} \quad 
  \alb^\nu(s) &= (\MMd^\nu - \I) \thb(s), \qquad
  \omb^\nu(s) = (\MMd^\nu - \I) \etw(s).
\end{aligned}
\end{equation}
%
If we note that we can write \( \MMd^\nu - \I = \prn{\frg + (-1)^\nu \enc} / 2rf^\nu \), we find that
%
\begin{equation}\label{eq:diagKKT}
\begin{aligned}
  \alb^\nu(s) &= \frac{\delta\mathbf{a}(s) + (-1)^\nu \enc \thb(s)}
                     {2rf^\nu},
  \qquad 
  \omb^\nu(s) = \frac{\delta\w + s \delta\etw(s) - (-1)^\nu \mathbf{a}(s)}
                     {2rf^\nu}, 
  \\
  \mu^\nu_{mm} &= \frac{\eqm_m}{2rf^\nu} 
    \left[ 
      \hat{A}(s) - c_m(s) (\delta\wm_m + s \delta\etwm_m(s))
      - \lambda \delta w_m
    \right. \\ &\hphantom{= \frac{\eqm_m}{2f^\nu} \big[}
    \left. {}
      + (-1)^\nu \prn{ 
        c_m(s) a_m(s) - [\encm \thbm(s)]_m
        - \delta\wm_m - s \delta\etwm_m(s)
        + \lambda a_m(0)
      }
    \right], 
\end{aligned}
\end{equation}
%
where \(\delta\) indicates mean subtraction and \(\eq \mathbf{a}(s) = \hat{A}(s)\).

@@

Under the scale transformation
%
\begin{equation}\label{eq:scale}
  \zeta * \MMd \equiv (1-\zeta) \MMd + \zeta \I ,
\end{equation}
%
the Laplace transform has the following scaling property
%
\begin{equation}\label{eq:laplacescale}
  \hat{A} \prn{\zeta s;\zeta * \MMd^\nu} = \hat{A} \prn{s; \MMd^\nu}.
\end{equation}
%
At \(s = 0\), it is scale invariant.
This means that in \cite{Lahiri2013synapse} we could take a pair of matrices that violates the ``diagonal'' constraints (second inequality of \eqref{eq:constri}) and use the scale transform \eqref{eq:scale} to construct a pair of matrices that satisfy the ``diagonal'' constraints and have the same area.
This allowed us to ignore the diagonal constraints.
We can't do that for \(s > 0\).

The corresponding symmetry here is scaling the shifted process from \cref{eq:lshiftpd}, which amounts to
%
\begin{equation}\label{eq:shiftscale}
  \zeta {\circledast}_{s} \MMd 
      \equiv (1 - \zeta) \MMd
      + \zeta \brk{(1 + s)\I - s \onev \eq} .
\end{equation}
%
Then we have
%
\begin{equation}\label{eq:lshiftscale}
  \hat{A} \prn{s; \MMd^\nu} 
    = \hat{A} \prn{0, \shift{\MMd}^\nu(s)}
    = \hat{A} \prn{0, \zeta * \shift{\MMd}^\nu(s)}
    = \hat{A} \prn{s, \zeta \circledast_s \MMd^\nu}.
\end{equation}
%
The problem here is that the lower bound, \(\MMdm^\nu_{ij} \geq 0\), 
is not invariant under this transformation, unlike the \(s = 0\) case.
Using this transformation to fix the upper bound can break the lower bound.

We might ask what conditions are required so that a model is fixable?
This means that the \(\zeta \circledast_s \) orbit of the model contains some valid models.
The conditions are
%
\begin{equation*}
\begin{alignedat}{5}
  [\zeta \circledast \MMd^\nu]_{ij}  
    &= \zeta \MMdm^\nu_{ij} - (1-\zeta) s \eqm_j 
    &&\geq 0 &
  \quad &\implies \quad &
  \zeta &\geq \frac{s \eqm_j}{\MMdm^\nu_{ij} + s \eqm_j} &
    &\forall \nu, i, j : i \neq j , \\
  \sum_{j : i \neq j} [\zeta \circledast \MMd^\nu]_{ij} 
    &= \zeta \lbm^\nu_i - (1-\zeta) s (1-\eqm_i) 
    &&\leq 1 &
  &\implies &
  \zeta &\leq \frac{1 + s (1-\eqm_i)}{\lbm^\nu_i + s (1-\eqm_i)} &
    \quad &\forall \nu, i ,
\end{alignedat}
\end{equation*}
%
where \(\lbm^\nu_i \equiv \sum_{j : i \neq j} \MMdm^\nu_{ij}\) is the inverse mean  lifetime of state \(i\).
The model is fixable if it is possible to find a \(\zeta\) that satisfies all of the above conditions:
%
\begin{equation}\label{eq:fixable}
  \frac{s \eqm_j}{\MMdm^\nu_{ij} + s \eqm_j} \leq \frac{1 + s (1-\eqm_k)}{\lbm^\mu_k + s (1-\eqm_k)}
  \quad \implies \quad
  \frac{\lbm^\mu_k - 1}{1 + s (1-\eqm_k)} \leq \frac{\MMdm^\nu_{ij}}{s \eqm_j} 
  \quad \forall \mu, \nu, i, j, k : i \neq j.
\end{equation}
%
Note that when \(\MMdm^\nu_{ij} = 0\) for some \(i,j \), this condition reduces to \(\lbm^\mu_k \leq 1\), the original diagonal constraint.
Thus, relaxing the constraints from ``the model is valid'' to ``the model is fixable'' doesn't help us prove anything about the topology.

@@

The relation of the Laplace transform to the shifted process from \cref{eq:lshiftpd,eq:lareashift} suggests an alternative approach: 
treat the off-diagonal components of \(\shift{\MMd}^\nu \) as the degrees of freedom and maximise the area instead.
The constraints on \(\shift{\MMdm}^\nu_{ij}\) are different from \cref{eq:constri}:
%
\begin{equation}\label{eq:lshiftconstr}
  \shift{\MMdm}^\nu_{ij} \geq s \eqm_j,
    \quad \forall \; \nu, i, j : i \neq j, \qquad
  \sum_{j: j \neq i} \shift{\MMdm}^\nu_{ij} \leq 1 + s (1 - \eqm_i).
    \quad \forall \; \nu, i.
\end{equation}
%
The diagonal elements are still given by \( \shift{\MMdm}^\nu_{ii} = 1 - \sum_{j: j \neq i} \shift{\MMdm}^\nu_{ij} \), but now they are allowed to be negative so long as \(\shift{\MMdm}^\nu_{ii} \geq - s (1 - \eqm_i)\).

>>>>

If the plasticity events occur at Poisson rate \(r\), the probability of \(n\) events occurring in time \(t\) is given by a Poisson distribution with mean \(rt\).
If we marginalise over \(n\) as well
%
\begin{equation}\label{eq:plastseqav}
\begin{aligned}
  P(\text{state}=i,t \mid \text{pot/dep},0)
    &= \sum_n \frac{(rt)^n}{n!} \e^{-rt} \eq  \MMd \potdep (f\pot \MMd \pot+f\dep \MMd \dep)^n \\
    &= \brk{ \eq  \MMd \potdep\, \e^{rt(f\pot \MMd \pot+f\dep \MMd \dep-\I) } }_i,
\end{aligned}
\end{equation}
%
where \(\eq\) is the steady state distribution of the continuous time transition matrix that appears in the exponential:
%
\begin{equation}\label{eq:eq}
  \eq\frg = 0,
  \qquad\text{where}\quad
  \frg = \sum_\nu r f^\nu (\MMd^\nu - \I)
    = r f\pot \MMd \pot + r f\dep \MMd \dep - r \I.
\end{equation}
%
It will be useful to introduce continuous time Markov processes corresponding to \(\MMd^\nu \):
%
\begin{equation*}
  \W^\nu = r f^\nu (\MMd^\nu - \I),
  \qquad
  \frg = \sum_{\nu} \W^\nu.
\end{equation*}
%

This results in
%
\begin{equation}\label{eq:overlapwt}
\begin{aligned}
  \av{\synid^1 \syn^1(t)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \e^{t\frg} \w, \\
  \av{\synid^1 \syn^1(\infty)} &= \eq (f\pot \MMd \pot-f\dep \MMd \dep)\, \onev\eq \w \\
         &= \eq (f\pot\onev-f\dep\onev)\, \eq \w \\
         &=  (f\pot-f\dep)\, \eq \w \\
         &=  \Delta f\, \eq \e^{t\frg} \w ,
\end{aligned}
\end{equation}
%
where \(\Delta f = f\pot - f\dep \).
Combining the expressions in \cref{eq:overlapwt} allows us to write the numerator of \cref{eq:SNRdef} as
%
\begin{equation}\label{eq:signal}
\begin{aligned}
  \av{\synid \cdt \syn(t)} - \av{\synid \cdt \syn(\infty)}
    &= \frac{N}{r} \eq \enc \, \e^{t \frg} \w , \\
    \text{where} \qquad
  \enc &= \sum_\nu (-1)^\nu \W^\nu
    = r f\pot \MMd\pot - r f\dep \MMd\dep - r \Delta f \I.
\end{aligned}
\end{equation}
%
Combining with \eqref{eq:noise} gives
%
\begin{equation}\label{eq:SNRcurveExact}
  \SNR(t) = \frac{\sqrt{N} \eq \enc\,\e^{t \frg}\w}
                 {r \sqrt{1-(\Delta f)^2(\eq \w)^2}}.
\end{equation}
%
The denominator will not play any role in what follows, as the models that maximize the various measures of memory performance all have some sort of balance between potentiation and depression, either with \(f\pot=f\dep\) or \(\eqm_+=\eqm_-\).
We can perform the maximisation in two steps.
First maximise the numerator at fixed \(\eq \w\).
Then maximise the ratio \wrt \(\Delta \pr = \eq\w\).
This will allow us to ignore the denominator until the very end.

We can then treat the off-diagonal elements of \(\MMd^\nu\) as the independent degrees of freedom, subject to these constraints, when maximising the SNR.
The diagonal elements are determined by setting the row sums to 1.
We then have
%
\begin{equation}\label{eq:derivpd}
  \pdiff{\MMdm^\mu_{ij}}{\MMdm^\nu_{mn}} 
      = \delta_{\mu\nu}\, \delta_{im}(\delta_{jn}-\delta_{jm}),
\end{equation}
%
It will sometimes be more convenient to use the off-diagonal elements of \(\W^\nu \) as the independent degrees of freedom.
Then
%
\begin{equation}\label{eq:wdof}
\begin{gathered}
  \Wm^\nu_{i j} \geq 0
    \quad \forall \; \nu, i, j : i \neq j, \qquad
  \sum_{j : j\neq i} \Wm^\nu_{ij} \leq r f^\nu
    \quad \forall \; \nu, i, \qquad
  \Wm^\nu_{ii} = - \sum_{j : j\neq i} \Wm^\nu_{ij}, \\
  \pdiff{}{\Wm^\nu_{ij}} = \frac{1}{rf^\nu} \pdiff{}{\MMdm^\nu_{ij}} 
    \quad \forall \; \nu, i, j : i \neq j, \qquad
  \pdiff{\Wm^\mu_{ij}}{\Wm^\nu_{mn}} 
      = \delta_{\mu\nu}\, \delta_{im}(\delta_{jn}-\delta_{jm}).
\end{gathered}
\end{equation}
%
Replacing \(\MMd\) with \(\W\) makes dimensional analysis easier and absorbs factors of \(f^\nu\) in several places.

It will also be convenient to define the differential operators
%
\begin{equation}\label{eq:pertfe}
  \pdiff{}{\frgm_{ij}} = \frac{1}{2rf\pot} \pdiff{}{\MMdm \pot_{ij}} + \frac{1}{2rf\dep} \pdiff{}{\MMdm \dep_{ij}},
  \qquad
  \pdiff{}{\encm_{ij}} = \frac{1}{2rf\pot} \pdiff{}{\MMdm \pot_{ij}} - \frac{1}{2rf\dep} \pdiff{}{\MMdm \dep_{ij}},
\end{equation}
%
which satisfy
%
\begin{equation}\label{eq:derivfe}
  \pdiff{\frgm_{ij}}{\frgm_{mn}} = \pdiff{\encm_{ij}}{\encm_{mn}} = \delta_{im}(\delta_{jn}-\delta_{jm}),
  \qquad
  \pdiff{\frgm_{ij}}{\encm_{mn}} = \pdiff{\encm_{ij}}{\frgm_{mn}} = 0.
\end{equation}
%

% If we wish to use the off-diagonal elements of \(\frg\) and \(\enc\) as the degrees of freedom, the constraints are
% %
% \begin{equation}\label{eq:constrfe}
% \begin{aligned}
%   \frgm_{i \neq j}   &\geq \abs{ \encm_{i \neq j} }, &\qquad
%   \sum_{j\neq i}\frgm_{ij} + (-1)^\mu \encm_{ij}  &\leq 2rf^\mu, \\
%   \sum_j \frgm_{ij} &=0, &
%   \sum_j \encm_{ij} &=0.
% \end{aligned}
% \end{equation}
% %

@@

We can also express this in terms of the shifted process in \cref{eq:larea}.
We can choose how to distribute the shift across \(\W \pot\) and \(\W \dep\).
Two choices from a continuum%
\footnote{We could choose \( \shift{\W}^\nu(s) = \W^\nu + s g^\nu (\onev \eq - \I) \), for any \(g^\nu \) with \( \sum_\nu g^\nu = 1 \).
It shifts \(\frg\) correctly and also shifts \( \shift{\enc}(s) = \enc + s \Delta g (\onev \eq - \I) \).
The two possibilities in \cref{eq:lshiftpd} come from \(g^\nu = \frac{1}{2}\) and \(g^\nu = f^\nu\) respectively.}
are:
%
\begin{equation}\label{eq:lshiftpd}
  \shift{\W}^\nu(s) = \W^\nu + \frac{s}{2} (\onev \eq - \I)
  \qquad \text{or} \qquad
  \shift{\W}^\nu(s) = \W^\nu + s f^\nu (\onev \eq - \I).
\end{equation}
%
The first choice leaves \( \shift{\enc} = \enc \), so it only affects the \(\etw\) piece of \cref{eq:larea}.
The second choice does not leave \(\enc\) invariant (in fact \( \shift{\enc}(s) = \enc + s \Delta f (\onev \eq - \I) \)), but because \( \eq (\onev \eq - \I) = 0 \) the shift does not make any contribution to \cref{eq:larea}.
Either way:
%
\begin{equation}\label{eq:lareashift}
  \hat{A}\prn{s; \W^\nu} = \hat{A}\prn{0; \shift{\W}^\nu(s)}.
\end{equation}
%
In other words, the laplace transform of the SNR is the area under the SNR for the shifted process.

Note that while \cref{eq:lshift} produces a valid continuous-time Markov process, \cref{eq:lshiftpd} does not always produce valid discrete-time Markov processes, \( \shift{\MMd}^\nu = \frac{\shift{\W}^\nu}{rf^\nu} + \I \), as the diagonal elements can become negative.
However, \(\shift{\W}^\nu \) is a valid continuous-time Markov process.

@@

Now we'll maximise \(\snrb(\tau)\) for some fixed \(\tau\), subject to the constraints \eqref{eq:constr}.
First, we will maximise the numerator of \eqref{eq:lsnr} holding \(\eq\w\) fixed.
We can maximise the ratio \wrt \(\eq\w\) later.
% From this point on, we work in units where \(r = 1\).

Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i(s) - \etwm_j(s))
        +\sum_{\nu i j} \mu^\nu_{ij} \prn{ \Wm^\nu_{ij} + r f^\nu \delta_{ij} }
        + \lambda \prn{ \Delta\pr - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where \(\Delta\pr\) is the constant value we are holding \(\eq\w\) at.
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\Wm^\nu_{ij}} = 0, \quad
  \mu^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu^\nu_{ij}} \geq 0, \quad
  \mu^\nu_{ij}\pdiff{\CL}{\mu^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
We have scaled the KKT multipliers by \(r f^\nu\) for later convenience.

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \pdiff{\CL}{\Wm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     + \prn{c_m(s) + (-1)^\nu} \brk{\etwm_m(s) - \etwm_n(s)} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     + \lambda \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
We can solve for the KKT multipliers by noting that
%
\begin{equation*}
  \mu^\nu_{ij} \Wm^\nu_{ij} = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \mu^\nu_{ii} \Wm^\nu_{ij} 
      = \mu^\nu_{ii} ( - \Wm^\nu_{ii}) = r f^\nu \mu^\nu_{ii}.
\end{equation*}
%
Then, with some new vectors defined:
%
\begin{equation}\label{eq:kktsol}
\begin{aligned}
  \mu^\nu_{mm} &= - \eqm_m \prn{ \albm^\nu_m(s) 
    + \lambda \ombm^\nu_m(0) 
    + \prn{{c}_m(s) + (-1)^\nu} \ombm^\nu_m(s)
    }, \\
  \mu^\nu_{mn} &= \eqm_m \big( 
      \brk{ \thbm_n(s) - \thbm_m(s) - \albm^\nu_m(s) }
    + \lambda \brk{ \etwm_n(0) - \etwm_m(0) - \ombm^\nu_m(0) } 
  \\ &\hphantom{= \eqm_m \big( }
    + \brk{{c}_m(s) + (-1)^\nu} 
        \brk{ \etwm_n(s) - \etwm_m(s) - \ombm^\nu_m(s) }
     \big), \\
  \text{where} \quad 
  \alb^\nu(s) &= \frac{\W^\nu \thb(s)}{rf^\nu}, \qquad
  \omb^\nu(s) = \frac{\W^\nu \etw(s)}{rf^\nu}.
\end{aligned}
\end{equation}
%
If we note that we can write \( \W^\nu = \prn{\frg + (-1)^\nu \enc} / 2 \), we find that
%
\begin{equation}\label{eq:diagKKT}
\begin{aligned}
  \alb^\nu(s) &= \frac{\delta\mathbf{a}(s) + (-1)^\nu \enc \thb(s)}
                     {2rf^\nu},
  \qquad 
  \omb^\nu(s) = \frac{\delta\w + s \delta\etw(s) - (-1)^\nu \mathbf{a}(s)}
                     {2rf^\nu}, 
  \\
  \mu^\nu_{mm} &= \frac{\eqm_m}{2rf^\nu} 
    \left[ 
      \hat{A}(s) - c_m(s) (\delta\wm_m + s \delta\etwm_m(s))
      - \lambda \delta w_m
    \right. \\ &\hphantom{= \frac{\eqm_m}{2f^\nu} \big[}
    \left. {}
      + (-1)^\nu \prn{ 
        c_m(s) a_m(s) - [\encm \thbm(s)]_m
        - \delta\wm_m - s \delta\etwm_m(s)
        + \lambda a_m(0)
      }
    \right], 
\end{aligned}
\end{equation}
%
where \(\delta\) indicates mean subtraction and \(\eq \mathbf{a}(s) = \hat{A}(s)\).

@@

% Under the scale transformation
% %
% \begin{equation}\label{eq:scale}
%   \zeta * \MMd \equiv (1-\zeta) \MMd + \zeta \I ,
% \end{equation}
% %
The Laplace transform has the following scaling property
%
\begin{equation}\label{eq:laplacescale}
  \hat{A} \prn{\zeta s;\zeta \W^\nu} = \hat{A} \prn{s; \W^\nu}.
\end{equation}
%
At \(s = 0\), it is scale invariant.
This means that in \cite{Lahiri2013synapse} we could take a pair of matrices that violates the ``diagonal'' constraints (second inequality of \cref{eq:constri}) and use the scale transform to construct a pair of matrices that satisfy the ``diagonal'' constraints and have the same area.
This allowed us to ignore the diagonal constraints.
We can't do that for \(s > 0\).

The corresponding symmetry here is scaling the shifted process from \cref{eq:lshiftpd}, which amounts to
%
\begin{equation}\label{eq:shiftscale}
  \zeta {\circledast}_{s} \W^\nu
      \equiv \zeta \W^\nu
      + (1 - \zeta) s f^\nu \brk{\I - \onev \eq} .
\end{equation}
%
Then we have
%
\begin{equation}\label{eq:lshiftscale}
  \hat{A} \prn{s; \W^\nu} 
    = \hat{A} \prn{0, \shift{\W}^\nu(s)}
    = \hat{A} \prn{0, \zeta \shift{\W}^\nu(s)}
    = \hat{A} \prn{s, \zeta \circledast_s \W^\nu}.
\end{equation}
%
The problem here is that the lower bound, \(\Wm^\nu_{ij} \geq 0\), 
is not invariant under this transformation, unlike the \(s = 0\) case.
Using this transformation to fix the upper bound can break the lower bound.

We might ask what conditions are required so that a model is fixable?
This means that the \(\zeta \circledast_s \) orbit of the model contains some valid models.
The conditions are
%
\begin{equation*}
\begin{alignedat}{5}
  [\zeta \circledast \W^\nu]_{ij}  
    &= \zeta \Wm^\nu_{ij} - (1-\zeta) s f^\nu \eqm_j 
    &&\geq 0 &
  \;\; &\implies \;\; &
  \zeta &\geq \frac{s \eqm_j}{\Wm^\nu_{ij} /  f^\nu + s \eqm_j} &
    &\forall \nu, i, j : i \neq j , \\
  \sum_{j : i \neq j} [\zeta \circledast \W^\nu]_{ij} 
    &= \zeta \lbm^\nu_i - (1-\zeta) s f^\nu (1-\eqm_i) 
    &&\leq r f^\nu &
  &\implies &
  \zeta &\leq \frac{r + s (1-\eqm_i)}{\lbm^\nu_i / f^\nu + s (1-\eqm_i)} &
    \quad &\forall \nu, i ,
\end{alignedat}
\end{equation*}
%
where \(\lbm^\nu_i \equiv \sum_{j : i \neq j} \Wm^\nu_{ij}\) is the inverse mean  lifetime of state \(i\).
The model is fixable if it is possible to find a \(\zeta\) that satisfies all of the above conditions:
%
\begin{equation}\label{eq:fixable}
  \frac{s \eqm_j}{\Wm^\nu_{ij} / f^\nu + s \eqm_j} \leq \frac{r + s (1-\eqm_k)}{\lbm^\mu_k / f^\nu + s (1-\eqm_k)}
  \quad \implies \quad
  \frac{\lbm^\mu_k - r f^\nu}{r + s (1-\eqm_k)} \leq \frac{\Wm^\nu_{ij}}{s \eqm_j} 
  \quad \forall \mu, \nu, i, j, k : i \neq j.
\end{equation}
%
Note that when \(\Wm^\nu_{ij} = 0\) for some \(i,j \), this condition reduces to \(\lbm^\mu_k \leq r f^\nu\), the original diagonal constraint.
Thus, relaxing the constraints from ``the model is valid'' to ``the model is fixable'' doesn't help us prove anything about the topology.

@@

The relation of the Laplace transform to the shifted process from \cref{eq:lshiftpd,eq:lareashift} suggests an alternative approach: 
treat the off-diagonal components of \(\shift{\W}^\nu \) as the degrees of freedom and maximise the area instead.
The constraints on \(\shift{\Wm}^\nu_{ij}\) are different from \cref{eq:constri}:
%
\begin{equation}\label{eq:lshiftconstr}
  \shift{\Wm}^\nu_{ij} \geq s f^\nu \eqm_j,
    \quad \forall \; \nu, i, j : i \neq j, \qquad
  \sum_{j: j \neq i} \shift{\Wm}^\nu_{ij} \leq r f^\nu + s f^\nu (1 - \eqm_i).
    \quad \forall \; \nu, i.
\end{equation}
%
The diagonal elements are still given by \( \shift{\Wm}^\nu_{ii} = - \sum_{j: j \neq i} \shift{\Wm}^\nu_{ij} \), but now they are be below \(-r f^\nu \) so long as \(\shift{\Wm}^\nu_{ii} \geq -r f^\nu - s f^\nu (1 - \eqm_i)\).

The Lagrangian we should consider is
%
\begin{equation}\label{eq:lshiftlagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i - \etwm_j)
        +\sum_{\nu i j} \mu^\nu_{ij}\prn{\Wm^\nu_{ij} + f^\nu (r + s) \delta_{ij} -  s f^\nu \eqm_j }
        &+ \lambda \prn{ \Delta\pr - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where all of the first-passage times are evaluated at \(s = 0\).
